Figures

### 2019-07-08 figures/07_model-selection.Rmd
fix labels, significance coloring

# plot tp model fixed effects summary
# summary(fit_tp)
gg_tp <- spread_draws(fit_tp, 
                     b_maxdepth, 
                     b_hu12vbaseflowvmean, 
                     b_phosphorusvfertilizervuse, 
                     b_buffervcultivatedvcrops) %>%
  tidyr::gather(key = "key", value = "value", -.chain, -.iteration, -.draw) %>%
  mutate(key = stringr::str_replace(key, "b_", "")) %>%
  left_join(pred_key, by = c("key" = "varv")) %>%
  mutate(key = factor(pretty, levels = c("Max depth", 
                     "Baseflow", 
                     "Fertilizer P input", 
                     "Buffer Ag"))) %>%
  group_by(key) %>%
  summarize(value = list(tibble::enframe(quantile(value, probs=c(0.05,0.5,0.95))))) %>% 
  unnest() %>%
  tidyr::spread(name, value) %>%
  rowwise() %>%
  mutate(signif = `5%` & `95%` > 0 | `5%` & `95%` < 0)

@@

```{r tp_re, fig.width=3.25, fig.height=4.5}
fit_tp$re$hu4vzoneid <- gsub("HU4_", "", fit_tp$re$hu4vzoneid)
gg_tp_re <- ggplot(data = fit_tp$re) +
  geom_pointrange(aes(x = hu4vzoneid, y = `50%`, 
                      ymin = `5%`, ymax = `95%`, color = signif)) +
  scale_color_manual(values = c("FALSE" = "black", "TRUE" = "red")) +
  geom_hline(yintercept = 0) +
  coord_flip() +
  cowplot::theme_cowplot() +
  theme(rect = element_rect(fill = "transparent")) +
  ylab("TP model, pasture RE slope") + theme(legend.position = 0)

@@

# plot tn model fixed effects summary
# summary(fit_tn)
gg_tn <- spread_draws(fit_tn, 
                     b_maxdepth, 
                     b_soilvorgvcarbon, 
                     b_nitrogenvfertilizervuse, 
                     b_buffervcultivatedvcrops) %>%
  tidyr::gather(key = "key", value = "value", -.chain, -.iteration, -.draw) %>%
  mutate(key = stringr::str_replace(key, "b_", "")) %>%
  left_join(pred_key, by = c("key" = "varv")) %>%
  mutate(key = factor(pretty, levels = c("Max depth", 
                     "Soil organic carbon", 
                     "Fertilizer N input", 
                     "Buffer Ag"))) %>%
  group_by(key) %>%
  summarize(value = list(tibble::enframe(quantile(value, probs=c(0.05,0.5,0.95))))) %>% 
  unnest() %>%
  tidyr::spread(name, value) %>%
  rowwise() %>%
  mutate(signif = `5%` & `95%` > 0 | `5%` & `95%` < 0)

@@

```{r tn_re, fig.width=3.25, fig.height=4.5}
# dotplot tn hu4 random effects
fit_tn$re$hu4vzoneid <- gsub("HU4_", "", fit_tn$re$hu4vzoneid)
gg_tn_re <- ggplot(data = fit_tn$re) +
  geom_pointrange(aes(x = hu4vzoneid, y = `50%`, 
                      ymin = `5%`, ymax = `95%`, color = signif)) +
  scale_color_manual(values = c("FALSE" = "black", "TRUE" = "red")) +
  geom_hline(yintercept = 0) +
  coord_flip() +
  cowplot::theme_cowplot() +
  theme(rect = element_rect(fill = "transparent")) +
  ylab("TN model, corn RE slope") + theme(legend.position = 0)

>>>>

# plot tp model fixed effects summary
# summary(fit_tp)
gg_tp <- spread_draws(fit_tp, 
                     b_maxdepth, 
                     b_hu12vbaseflowvmean, 
                     b_phosphorusvfertilizervuse, 
                     b_buffervcultivatedvcrops) %>%
  tidyr::gather(key = "key", value = "value", -.chain, -.iteration, -.draw) %>%
  mutate(key = stringr::str_replace(key, "b_", "")) %>%
  left_join(pred_key, by = c("key" = "varv")) %>%
  mutate(key = factor(pretty, levels = c("Max depth", 
                     "Baseflow", 
                     "Fertilizer P input", 
                     "Buffer Ag"))) %>%
  group_by(key) %>%
  summarize(value = list(tibble::enframe(quantile(value, probs=c(0.05,0.5,0.95))))) %>% 
  unnest() %>%
  tidyr::spread(name, value) %>%
  rowwise() %>%
  mutate(signif = (`5%` > 0 & `95%` > 0)| (`5%` < 0 & `95%` < 0))

@@

```{r tp_re, fig.width=3.25, fig.height=4.5}
fit_tp$re$hu4vzoneid <- gsub("HU4_", "", fit_tp$re$hu4vzoneid)
gg_tp_re <- ggplot(data = fit_tp$re) +
  geom_pointrange(aes(x = hu4vzoneid, y = `50%`, 
                      ymin = `5%`, ymax = `95%`, color = signif)) +
  scale_color_manual(values = c("FALSE" = "black", "TRUE" = "red")) +
  geom_hline(yintercept = 0) +
  coord_flip() +
  cowplot::theme_cowplot() +
  theme(rect = element_rect(fill = "transparent")) +
  ylab("TP model, pasture RE slope") + xlab("Zone ID") +
  theme(legend.position = 0)

@@

# plot tn model fixed effects summary
# summary(fit_tn)
gg_tn <- spread_draws(fit_tn, 
                     b_maxdepth, 
                     b_soilvorgvcarbon, 
                     b_nitrogenvfertilizervuse, 
                     b_buffervcultivatedvcrops) %>%
  tidyr::gather(key = "key", value = "value", -.chain, -.iteration, -.draw) %>%
  mutate(key = stringr::str_replace(key, "b_", "")) %>%
  left_join(pred_key, by = c("key" = "varv")) %>%
  mutate(key = factor(pretty, levels = c("Max depth", 
                     "Soil organic carbon", 
                     "Fertilizer N input", 
                     "Buffer Ag"))) %>%
  group_by(key) %>%
  summarize(value = list(tibble::enframe(quantile(value, probs=c(0.05,0.5,0.95))))) %>% 
  unnest() %>%
  tidyr::spread(name, value) %>%
  rowwise() %>%
  mutate(signif = (`5%` > 0 & `95%` > 0)| (`5%` < 0 & `95%` < 0))

@@

```{r tn_re, fig.width=3.25, fig.height=4.5}
# dotplot tn hu4 random effects
fit_tn$re$hu4vzoneid <- gsub("HU4_", "", fit_tn$re$hu4vzoneid)
gg_tn_re <- ggplot(data = fit_tn$re) +
  geom_pointrange(aes(x = hu4vzoneid, y = `50%`, 
                      ymin = `5%`, ymax = `95%`, color = signif)) +
  scale_color_manual(values = c("FALSE" = "black", "TRUE" = "red")) +
  geom_hline(yintercept = 0) +
  coord_flip() +
  cowplot::theme_cowplot() +
  theme(rect = element_rect(fill = "transparent")) +
  ylab("TN model, corn RE slope") + xlab("Zone ID") + 
  theme(legend.position = 0)
